---
title: "My Text Mining Repository"
author: "Amin Rigi"
output: github_document
always_allow_html: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Last Update: `r Sys.Date()`

After few months of text mining for few industry projects, I decided to neatly pack the functions that I used the most into a single place. I eventually will update this repository. I start with simple text cleaning and tidy text mining and then will add ML-based tools. 

Required packages:

* [`tm`](https://cran.r-project.org/web/packages/tm/index.html)
* [`tidytext`]()
* [`tidyverse`]()
* [`wordcloud`]()
* [`wordcloud2`]()
* [`topicmodels`]()
* [`ldatuning`]()
* [`lsa`]()



## Text pre-processing 

Text pre-processing consists of several steps such as removal of stopwords, numerical characters, and punctuation. Few other steps are fixing encoding, consistency between US and UK English, and dealing with exceptional situations. The function [`tm/pre-process`](https://github.com/aminrigi/Text-Mining/blob/master/tm/pre_process.R) will do this. Let's clean the first chapter of [The Little Prince](http://users.uoa.gr/~nektar/arts/tributes/antoine_de_saint-exupery_le_petit_prince/the_little_prince.htm) using [`pre-process.R`](https://github.com/aminrigi/Text-Mining/blob/master/tm/pre_process.R).

```{r warning = FALSE, error = FALSE, message=FALSE}
source("tm/pre_process.R")

myText = "Once when I was six years old I saw a magnificent picture in a book, called True Stories from Nature, about the primeval forest. It was a picture of a boa constrictor in the act of swallowing an animal. Here is a copy of the drawing.
In the book it said: Boa constrictors swallow their prey whole, without chewing it. After that they are not able to move, and they sleep through the six months that they need for digestion. I pondered deeply, then, over the adventures of the jungle. And after some work with a colored pencil I succeeded in making my first drawing. My Drawing Number One. It looked something like this:
I showed my masterpiece to the grown-ups, and asked them whether the drawing frightened them. But they answered: Frighten? Why should any one be frightened by a hat? 

My drawing was not a picture of a hat. It was a picture of a boa constrictor digesting an elephant. But since the grown-ups were not able to understand it, I made another drawing: I drew the inside of a boa constrictor, so that the grown-ups could see it clearly. They always need to have things explained. My Drawing Number Two looked like this:
The grown-ups' response, this time, was to advise me to lay aside my drawings of boa constrictors, whether from the inside or the outside, and devote myself instead to geography, history, arithmetic, and grammar. That is why, at the age of six, I gave up what might have been a magnificent career as a painter. I had been disheartened by the failure of my Drawing Number One and my Drawing Number Two. Grown-ups never understand anything by themselves, and it is tiresome for children to be always and forever explaining things to them. So then I chose another profession, and learned to pilot airplanes. I have flown a little over all parts of the world; and it is true that geography has been very useful to me. At a glance I can distinguish China from Arizona. If one gets lost in the night, such knowledge is valuable. In the course of this life I have had a great many encounters with a great many people who have been concerned with matters of consequence. I have lived a great deal among grown-ups. I have seen them intimately, close at hand. And that hasn't much improved my opinion of them.

Whenever I met one of them who seemed to me at all clear-sighted, I tried the experiment of showing him my Drawing Number One, which I have always kept. I would try to find out, so, if this was a person of true understanding. But, whoever it was, he, or she, would always say: That is a hat.

Then I would never talk to that person about boa constrictors, or primeval forests, or stars. I would bring myself down to his level. I would talk to him about bridge, and golf, and politics, and neckties. And the grown-up would be greatly pleased to have met such a sensible man."

myStopwords = c("have", "whoever")

cleaned_text = pre_process(txt = myText, myStopwords = myStopwords)

print(cleaned_text)

```

## Wordcloud of a Text

Functions [`tm/plot_wordCloud.R`](https://github.com/aminrigi/Text-Mining/blob/master/tm/plot_feelingCloud.R) and [`tm/plot_wordCloud2.R`](https://github.com/aminrigi/Text-Mining/blob/master/tm/plot_feelingCloud2.R) can be used for plotting wordcloud or wordcloud2 for a chunk of text. Here's the wordcloud for first chapter of *The Little Prince*:

```{r warning = FALSE, error = FALSE, message=FALSE}

source("tm/plot_wordCloud2.R")
plot_wordCloud2(cleaned_text, 20)

source("tm/plot_wordCloud.R")
plot_wordCloud(cleaned_text, 20)

```


## [Feeling Cloud](https://github.com/aminrigi/Feeling-Cloud) of a Text
Functions [`tm/plot_feelingCloud.R`](https://github.com/aminrigi/Text-Mining/blob/master/tm/plot_feelingCloud.R) and [`tm/plot_feelingCloud2.R`](https://github.com/aminrigi/Text-Mining/blob/master/tm/plot_feelingCloud2.R) are for plotting feeling cloud of a text. For more on feeling cloud take a look at [here](https://github.com/aminrigi/Feeling-Cloud).

```{r warning = FALSE, error = FALSE, message=FALSE}
source("tm/plot_feelingCloud.R")
plot_feelingCloud(cleaned_text, 20)

```


Comparing feeling cloud of the text with its word cloud may give you some idea about feeling cloud.


## Sentiment Analysis
Function [`tm/plot_sentiments`](https://github.com/aminrigi/Text-Mining/blob/master/tm/plot_sentiments.R) plots sentiments for a text. 

```{r warning = FALSE, error = FALSE, message=FALSE}
source("tm/plot_sentiments.R")
plot_sentiments(cleaned_text, "bing")

plot_sentiments(cleaned_text, "nrc")

plot_sentiments(cleaned_text, "loughran")

```


## Finding Document-Term Matrix

Document-term matrix or dtm is one of the most useful tools that maps a set of documents to vector space model and enables us to do variety of text mining algorithms. Function [`tm/get_dtm`](https://github.com/aminrigi/Text-Mining/blob/master/tm/get_dtm.R) gets a vector of charachters. It is assumed the vector is already cleaned using [`tm/pre_process`](https://github.com/aminrigi/Text-Mining/blob/master/tm/pre_process.R) (we really don't want to pass unclean text to get_dtm!). The document-term matrix maps a set of documents into the vector space model. In other words, each document will be represented by a vector (a row in dtm). A good source to know more about text mining in R and vector space modeling is [`Data Science Mojo`](https://www.youtube.com/watch?v=4vuw0AsHeGw&index=1&list=PL8eNk_zTBST8olxIRFoo0YeXxEOkYdoxi). 




## Finding topics

The data





To Be Continued...
